Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-07-20 GNproofcolumns.tex
clarified GNproofcolumns

The algorithm above has a $1$ in every $(r, a_r)$, with $0$s above it and $0$s in all subsequent (in the $<_i$ order) entries in the $r^{th}$ row. It remains to check the columns not in $I_i$.

@@

Suppose $a_m + 1 < a_{m+1}$. That is, two consecutive propagators, $p_m$ and $p_{m+1}$ do not contribute consecutive indicies. (Without loss of generality, assume that $m$ is the smallest integer for which this is true.) We claim at the vertices in the cyclic interval $[a_m+1, a_{m+1}-1]$ are also columns of $0$s in $D(W)$. First note that they only support propagators in $\cP_m$. Indeed, if $v \in [a_m+1, a_{m+1}-1]$, and $v$ supported such a propagator, $q \in \Prop(v) \setminus \cP_m$, then $q$ would not have contributed to $I_i$ by the time the algorithm reached $v$, forcing $q$ to contribute either after $p_m$ and before $p_{m+1}$, which is a contradiction, or $q = p_{m+1}$, which contradicts $v < a_{m+1}$.

Therefore, for column $\vec{v}$ to have a non-zero entry, there must exists a $q$ that contributes after $p_m$ supported on an $a_{r_1}$ (with $r_1 < m$) and a sequence $\{a_{r_1} \ldots a_{r_j}, v\}$ such that each contibuting propagator is supported on the next assigned vertex in the series, $p_{r_i} \in \Prop(a_{r_{i+1}})$ and $p_{r_j} \in \Prop(v)$.\sanote{Key condition to check that I haven't missed any cases.} 
We show that this cannot happen. Note that when $p_{r_1}$ contributes $I_i(p_{r_1}) = a_{r_1}$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_{r_1}$ i.e. clockwise-most amongst propagators in the set $\cP \setminus \cP_{r_1-1}$. Therefore, if $q$ is assigned after $p_{r_1}$ but also supported on $a_{r_1}$, $q$ must be inside $p_{r_1}$ in the $a_{r_1} -1$ ordering. However, we know that $p_{r_1}$ is also supported on $a_{r_2} >_i a_{r_2}$. This either means that $q$ is also supported on $a_{r_2}$, in which case, we may start the above sequence from $a_{r_2}$, or that $q$ contributes a vertex in the interval $[a_{r_1} +1,a_{r_2} -1]$, which implies that $q$ contributes before $p_{m+1}$, which is a contradition.

>>>>

Note that if $p_s \in \Prop(a_r)$ with $r < s$, step 2 of this algorithm means that for all $v \in V(p_r)$ that come after $a_r$ ($a_r <_i v$) the entry $x_{s, v}$ is non-zero.
Upon termination of the algorithm above, $D(W)$ has a $1$ in every $(r, a_r)$, with $0$s above it and $0$s in all subsequent (in the $<_i$ order) entries in the $r^{th}$ row. It remains to check the columns not in $I_i$.

@@

Suppose $a_m + 1 < a_{m+1}$. That is, two consecutive propagators, $p_m$ and $p_{m+1}$ do not contribute consecutive indicies. (Without loss of generality, assume that $m$ is the smallest integer for which this is true.) We claim at the vertices in the cyclic interval $[a_m+1, a_{m+1}-1]$ are also columns of $0$s in $D(W)$. First note that they only support propagators in $\cP_m$. Indeed, if $v \in [a_m+1, a_{m+1}-1]$, and $v$ supported such a propagator, $q \in \Prop(v) \setminus \cP_m$, then $q$ would not have contributed to $I_i$ by the time the algorithm reached $v$, forcing $q$ to contribute either after $p_m$ and before $p_{m+1}$, which forces $q = p_{m+1}$, which contradicts $v < a_{m+1}$.

Therefore, for column $\vec{v}$ to have a non-zero entry, there must exists a $q$ that contributes after $p_m$ supported on an $a_{r_1}$ (with $r_1 < m$) and a an increasing sequence $\{a_{r_1} <_i \ldots <_i a_{r_j} <_i v\}$ such that each contibuting propagator is supported on the next assigned vertex in the series, $p_{r_i} \in \Prop(a_{r_{i+1}})$ and $p_{r_j} \in \Prop(v)$.\sanote{Key condition to check that I haven't missed any cases.} 
We show that this cannot happen. Note that when $p_{r_1}$ contributes $I_i(p_{r_1}) = a_{r_1}$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_{r_1}$ i.e. clockwise-most amongst propagators in the set $\cP \setminus \cP_{r_1-1}$. Therefore, if $q$ is assigned after $p_{r_1}$ but also supported on $a_{r_1}$, $q$ must be inside $p_{r_1}$ in the $a_{r_1} -1$ ordering. However, we know that $p_{r_1}$ is also supported on $a_{r_2} >_i a_{r_1}$. This either means that $q$ is also supported on $a_{r_2}$, in which case, we may start the above sequence from $a_{r_2}$, or that $q$ contributes a vertex in the interval $[a_{r_1} +1,a_{r_2} -1]$, which implies that $q$ contributes before $p_{m+1}$, which is a contradition.
